---
title: "Data Exploration"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data

In a study conducted by the National Institutes of Health, 109 clinically depressed patients were separated into three groups, and each group was given one of two active drugs (imipramine or lithium) or no drug at all. For each patient, the dataset contains the treatment used, the outcome of the treatment, and several other interesting characteristics.

Here is a summary of the variables in our dataset:

* Hospt: The patient's hospital, represented by a code for each of the 5 hospitals (1, 2, 3, 5, or 6)
* Treat: The treatment received by the patient (Lithium, Imipramine, or Placebo)
* Outcome: Whether or not a recurrence occurred during the patient's treatment (Recurrence or No Recurrence)
* Time: Either the time in days till the first recurrence, or if a recurrence did not occur, the length in days of the patient's participation in the study.
* AcuteT: The time in days that the patient was depressed prior to the study.
* Age: The age of the patient in years, when the patient entered the study.
* Gender: The patient's gender (1 = Female, 2 = Male)

Read-in data 
```{r }
load("data/depression.RData")
```

Get a summary of each column in the dataset. 
```{r depression}
summary(depression)
```


Get information about class, type and size of the dataset. 
```{r}
str(depression)
```


Recode variables:
```{r}
depression$Gender = replace(depression$Gender,depression$Gender==1,'Female');
depression$Gender = replace(depression$Gender,depression$Gender==2,'Male');
table(depression$Gender)
```




