---
title: "Tallying Data and Pie Charts"
---

<style>
body {
text-align: justify}
</style>

### Summarise data and make charts
A survey that asked 1,200 U.S. college students about their body perception also asked the following question:

"With whom do you find it easiest to make friends?" (opposite sex, same sex or no difference).

In this activity we will use the collected data to:

* learn how to tally our data into a table of counts and percents.
* learn how to produce a pie chart.

Load required dataset:
```{r }
load("data/friends.RData")
```

Get a summary table of the data:
```{r }
t = table(friends$Friends)
t
```

Get a summary table, with the proportion of each category. 
```{r }
prop = prop.table(t)
prop
```

Get a summary table, with the percentage of each category. 
```{r }
pct = prop.table(t) * 100
pct
```

Create a pie-chart
```{r }
pie(t)
```

Create a pie-chart using the percentages. First round the percentages. 
```{r }
pf = round(pct, 1)
pf
```

Next we will create a label that will include the category name and the percent as the labels for each section of the pie chart. R defaults to alphabetical order for tables and graphic creation so if you create your own labels list the names accordingly.

```{r }
lbl = paste(c("No difference", "Opposite sex", "Same sex"), pf, "%", sep = " ")
lbl
```

Finally, create the pie chart with the new label added
```{r }
pie(t,label=lbl)
```

